Dataset of operator-client dialogues aligned with knowledge-base queries

### 2016-06-28 paper.tex
Update on Overleaf.

\maketitle

\OP{Fill missing values about the dataset collected so far} \\
\OP{describe the dataset,apologize for not having the dataset collected - promise for camera ready version.} \\
\OP{grammar check} \\

>>>>

\maketitle
\OP{Fill missing values about the dataset collected so far} \\
\OP{describe the dataset,apologize for not having the dataset collected - promise for camera ready version.} \OD{You don't need to apologize, just state that. You can, but don't need to say how many you currently have}\\
\OP{grammar check} \\
